Increasing Chlorophyll *a* Amid Stable Nutrient Concentrations in Rhode Island Lakes and Reservoirs

### 2019-09-26 manuscript/manuscript.Rmd
more review edits

### Linear regression on annual means

Testing for a regression slope being different than zero can be used to test for monotonic trends in water quality data [@helsel2002statistical].  We used these standard procedures to test for positive or negative trends in lake temperature, chlorophyll *a*, TN, TP and TN:TP.  For each parameter, we fit a regression line to the z-scores as a function of year and tested the null hypothesis that no trend existed (e.g. $\beta$~1~ = 0).

>>>>

### Linear regression on annual mean z-scores

Testing for a regression slope being different than zero can be used to test for monotonic trends in water quality data [@helsel2002statistical].  We used these standard procedures to test for positive or negative trends in lake temperature, chlorophyll *a*, TN, TP and TN:TP.  For each parameter, we fit a regression line to the z-scores as a function of year and tested the null hypothesis that no trend existed (e.g. $\beta$~1~ = 0). Traditionally, trends would be determined by assessing "significance" but recent guidelines suggest not using arbitrary p-value cut-offs to assesses significance [@wasserstein2016asa].  Our interpretation of the trends attempts to follow this advice and we assess trends with the information provided by the magnitude of the slopes, the p-values, and our understanding of the processes involved.
